Irt plot extra

### 2022-02-22 manuscript.Rmd
Table 5&6: Greek symbols and footnote updated

CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
CFa.matrix[1,] = c("Five factor model:25", 
                   apa(cfa.sum.1$FIT[6],2,T), 
                   apa(cfa.sum.1$FIT[7],2,T), 
                   apa(cfa.sum.1$FIT[19],2,F), 
                   apa(cfa.sum.1$FIT[20],2,T),
                   apa(cfa.sum.1$FIT[27],2,T),
                   apa(cfa.sum.1$FIT[28],2,T),
                   apa(cfa.sum.1$FIT[29],2,T),
                   apa(cfa.sum.1$FIT[35],2,T))

@@

```{r tabCfa, results='asis'}
apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: five factor model with 25 items and five factor model with 23 items. The second model attained the best fit.", align = "c", landscape = T, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
```

@@

colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "Chi-Square Difference", "df difference*", "p")

@@

```{r InvarianceTab, results='asis'}
apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize" )

>>>>

CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
colnames(CFa.matrix) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
CFa.matrix[1,] = c("Five factor model:25", 
                   apa(cfa.sum.1$FIT[6],2,T), 
                   apa(cfa.sum.1$FIT[7],2,T), 
                   apa(cfa.sum.1$FIT[19],2,F), 
                   apa(cfa.sum.1$FIT[20],2,T),
                   apa(cfa.sum.1$FIT[27],2,T),
                   apa(cfa.sum.1$FIT[28],2,T),
                   apa(cfa.sum.1$FIT[29],2,T),
                   apa(cfa.sum.1$FIT[35],2,T))

@@

```{r tabCfa, results='asis'}
apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: five factor model with 25 items and five factor model with 23 items. The second model attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
```

@@

colnames(Invariance.table) <- c("$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper", "$\\Delta$ $\\chi^{2}$", "$\\Delta$ df*", "p")

@@

```{r InvarianceTab, results='asis'}
apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize", escape=F )
